SS finding report

### 2021-11-28 experiments/0_ss_finding/report.Rmd
updates

ss_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_SS_data.RDS"))
stab_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_stab_data.RDS"))

@@

```{r}
plot_ss_result3(ss_9s, 1)
plot_ss_result3(ss_9s, 8)
plot_ss_result4(ss_9s, 1, 8)
```

>>>>

ss_2s <- readRDS(here("experiments/0_ss_finding/data/2_strain_SS_data.RDS"))
stab_2s <- readRDS(here("experiments/0_ss_finding/data/2_strain_stab_data.RDS")) %>%
  mutate(num_strains = 2)
ss_3s <- readRDS(here("experiments/0_ss_finding/data/3_strain_SS_data.RDS"))
stab_3s <- readRDS(here("experiments/0_ss_finding/data/3_strain_stab_data.RDS")) %>%
  mutate(num_strains = 3)
ss_6s <- readRDS(here("experiments/0_ss_finding/data/6_strain_SS_data.RDS"))
stab_6s <- readRDS(here("experiments/0_ss_finding/data/6_strain_stab_data.RDS")) %>%
  mutate(num_strains = 6)
ss_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_SS_data.RDS"))
stab_9s <- readRDS(here("experiments/0_ss_finding/data/9_strain_stab_data.RDS")) %>%
  mutate(num_strains = 9)

all_stab <- stab_2s %>%
  bind_rows(stab_3s) %>%
  bind_rows(stab_6s) %>%
  bind_rows(stab_9s)

@@

```{r}
plot_ss_result3(ss_9s, 1)
plot_ss_result3(ss_9s, 13)
plot_ss_result4(ss_9s, 1, 13)

plot_ss_result3(ss_3s, 1)
plot_ss_result3(ss_3s, 13)
plot_ss_result4(ss_3s, 1, 13)

plot_ss_result5(ss_2s, 15,
                ss_9s, 15)
plot_ss_result5(ss_3s, 15,
                ss_9s, 15)
plot_ss_result5(ss_6s, 15,
                ss_9s, 15)

CB_vars <- unique(all_stab$CB_var_gmax_s)
SB_vars <- unique(all_stab$SB_var_gmax_s)

CB_all_stab <- all_stab %>%
  filter(SB_var_gmax_s == 0) %>%
  mutate(var_treat = "CB",
         var_gmax = CB_var_gmax_s)

SBPB_all_stab <- all_stab %>%
  filter(CB_var_gmax_s == 0) %>%
  mutate(var_treat = "SB-PB",
         var_gmax = SB_var_gmax_s)

for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
                   SB_var_gmax_s = sort(SB_vars))
CBSBPB_all_stab <- all_stab %>%
  right_join(for_join) %>%
  mutate(var_treat = "CB-SB-PB",
         var_gmax = CB_var_gmax_s)

all_stab_results <- CB_all_stab %>%
  bind_rows(SBPB_all_stab) %>%
  #  bind_rows(results3) %>%
  # bind_rows(results4) %>%
  bind_rows(CBSBPB_all_stab)

all_stab_results <- all_stab_results %>%
  mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))

all_stab_results_small <- select(all_stab_results, -7:-12)
```

```{r}
all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as.factor(num_strains))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)
```

```{r}
all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min_log,
             ymax = hyst_max_log,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_grid(num_strains ~ var_treat, scales = "free_y") +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

```{r}
all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax,
             col = as.factor(num_strains))) +
  geom_line(aes(y = hyst_min_log)) +
  geom_line(aes(y = hyst_max_log)) +
  facet_wrap( ~ var_treat, scales = "free_y", nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    #strip.background = element_blank(),
    #strip.text.x = element_blank()
  )
